### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
added the hypothesis 4 (3) models.

```{r Hypothesis 3 Model}
# intercept only model to check the within and between group variance.
H3_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H3))

@@

A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 3.

@@

@@

>>>>

```{r Hypothesis 2 Model}
# intercept only model to check the within and between group variance.
H3_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H3))

@@

A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.

@@

```{r Hypothesis 3 Main Test}
## The main model to test hypothesis 3, through a logistic regression model.
H4_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_H4_avg))

# and for omega
H4_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
                                     omega.tot_avg, family = binomial(), 
                                     data = data_H4_avg))

# alpha says negative, omega says positive, neither are significant though.

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H4_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_H4_multiple))

# and for omega
H4_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1|g), family = 
                                                  binomial(), data = 
                                                  data_H4_multiple))

# same as for non-multilevel model

# running a random slope multilevel logistic model
H4_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_H4_multiple))

# and for omega
H4_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1 + omega.tot|g), 
                                                family = binomial(), data =
                                                data_H4_multiple))

# alpha did not converge, and omega shows no significant effect.
```
